Weather Data Integration and Assimilation System\\

### 2020-02-10 results/sec_0-introduction.tex
Wrap Results chapter
Replaced work_load

This chapter includes performance study of the \acrshort{wdias}. In the first section \ref{se:test_plan} describes the planned method of testing the system.
In the next section \ref{se:work_load} describes the logic behind creating the workload to do the performance testing planned in \ref{se:test_plan}.
Following section \ref{se:observations} includes the results observed while performance study. And summarised the observations in the next section \ref{se:conclusion}.

\dbc{Use formal titles like experimental setup, workload, performance analysis.}

>>>>

This chapter includes performance study of the \acrshort{wdias}. In the first section \ref{se:test_plan} describes the planned method of testing the system.
In the next section \ref{se:workload} describes the logic behind creating the workload to do the performance testing planned in \ref{se:test_plan}.
Following section \ref{se:observations} includes the results observed while performance study. And summarised the observations in the next section \ref{se:discussion}.

### 2020-02-10 results/sec_3-observations.tex
Replaced work_load

According the \ref{se:test_plan} section, this section includes the observations after performing the test plans on the \acrshort{wdias} system setup and test plan test up which is explained in the \ref{se:work_load}.

>>>>

According the \ref{se:test_plan} section, this section includes the observations after performing the test plans on the \acrshort{wdias} system setup and test plan test up which is explained in the \ref{se:workload}.
